### 2024-08-25 docs/manuscript.tex
Updating manuscript with github link.

\textbf{Pre-registration:} This study's desired sample size, included variables, hypotheses, and
planned analyses were pre-registered on the Open Science Framework
%(https://doi.org/10.17605/OSF.IO/92PTZ)
prior to any unpublished data being collected \cite{gardner2024}.

@@

The author department names were mapped to the closest associated
``fields of study'' listed by the National Science Foundation
\cite{fields2014}. We analysed fields at three different hierarchical
levels, firstly the specific fields (e.g. ``genetics'', ``computer
science'', ``bioinformatics'' etc). These are mapped to general fields
within the ``fields of study'' classification (e.g. biological
sciences, computer sciences etc). We have further mapped these to
expertise type, the \textbf{development experts}, \textbf{domain
  experts} and \textbf{interdisciplinary experts}. The development
experts are from fields such as computer science, mathematics and
engineering, they are expected to bring expertise in software
engineering and mathematical modeling of biological problems. The
domain experts are drawn from the biological and health sciences and
are expected to have detailed knowledge of the subject area and be
invested in producing high performance software for their own
research. The interdisciplinary experts are drawn from
interdisciplinary subjects such as bioinformatics and biomathematics,
and from researchers who list both development and domain expertise in
their addresses. We have treated some fields as essentially
synonymous, for example departments of ``Computational Biology'' was
mapped to ``Bioinformatics''.

@@

\textbf{Statistical analysis:} The accuracy data is derived from
benchmarks using a diverse number of metrics that include sensitivity,
specificity, PPV, FDR, error rates, AUROC, MCC and others
\cite{weber2019essential}. The number of tools ranked in any benchmark
ranged from 3 to 50. In order to obtain a representative measure of
accuracy for a field that transcends diverse accuracy measures and
numbers of ranked tools we elected to use ranks and a
bootstrapping strategy.  We randomly sample with replacement sets of
200 tools (from the total of 498), a benchmark that includes each tool
is selected at random and the number of times the tool ``won'' against
another tool is recorded, as is the total number of pairwise
comparisons that were made. These counts of wins and total comparisons
are transferred to the corresponding specific, general and expertise
areas. This is repeated 1,000 times, and allows a way to estimate the
mean proportions of wins allocated to each field, and the 95\%
confidence interval (Figure~\ref{fig:fig2}A). We have also computed a
Z-score for each field using the below equation. This measures the
number of standard deviations the mean number of wins is from the
expected null value of 0.5 for randomly grouped tools
(Figure~\ref{fig:fig2}B).

@@

Add a GitHub Repo...

>>>>

~~~~\textbf{Pre-registration:} This study's desired sample size, included variables, hypotheses, and
planned analyses were pre-registered on the Open Science Framework
%(https://doi.org/10.17605/OSF.IO/92PTZ)
prior to any unpublished data being collected \cite{gardner2024}.

@@

The author department names were mapped to the closest associated
``fields of study'' listed by the National Science Foundation
\cite{fields2014}. We analysed fields at three different hierarchical
levels, firstly the specific fields (e.g. ``genetics'', ``computer
science'', ``bioinformatics'' etc). These are then mapped to more
general fields within the ``fields of study'' classification
(e.g. ``biological sciences'', ``computer sciences'' etc). We have
further mapped these to three expertise types, the \textbf{development
  experts}, \textbf{domain experts} and \textbf{interdisciplinary
  experts}. The development experts are from fields such as computer
science, mathematics and engineering, they are expected to bring
development-pertinent expertise in software engineering and
mathematical modeling of biological problems. The domain experts are
drawn from the biological and health sciences and are expected to have
detailed knowledge of the subject area and be invested in producing
high-performing software for their research. The interdisciplinary
experts are drawn from interdisciplinary subjects such as
bioinformatics, biostatistics and biomathematics. Additionally the
researchers who list both development and domain expertise in their
addresses (e.g. ``Computer Science'' and ``Genetics''). We have treated some fields as essentially synonymous, for
example departments of ``Computational Biology'' was mapped to
``Bioinformatics'', and ``Genomics'' is mapped to ``Genetics''.

@@

\textbf{Statistical analysis:} The accuracy data is derived from
benchmarks using a diverse number of metrics that include sensitivity,
specificity, PPV, FDR, error rates, AUROC, MCC and others
\cite{weber2019essential}. The number of tools ranked in any benchmark
ranged from 3 to 50. In order to obtain a representative measure of
accuracy for a field that transcends diverse accuracy measures and
numbers of ranked tools we elected to use ranks and a
bootstrapping strategy.  We randomly sample with replacement sets of
200 tools (from the total of 498), a benchmark that includes each tool
is selected at random and the number of times the tool ``won'' against
another tool is recorded, as is the total number of pairwise
comparisons that were made. These counts of wins and total comparisons
are transferred to the corresponding specific, general and expertise
areas. This is repeated 1,000 times, and allows a way to estimate the
mean proportions of wins allocated to each field, and a 95\%
confidence interval for this value (Figure~\ref{fig:fig2}A). We also compute a
Z-score for each field using the below equation. This measures the
number of standard deviations the mean number of wins is from the
expected null value of 0.5 for randomly grouped tools
(Figure~\ref{fig:fig2}B).

@@

The data, scripts, figures and manuscript draft files are availble at the GitHub repository:\\
\href{https://github.com/ppgardne/departments-software-accuracy}{https://github.com/ppgardne/departments-software-accuracy}
